A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
s/and than/and then/

We use random search to tune the hyperparameters of the model, setting the ranges for search for each hyperparameter heuristically (and validating the reasonableness of the ranges on the development set), and than launching eight copies of each experiment each with newly sampled hyperparameters from those ranges. Table~\ref{tab:hyperparams} below shows the hyperparameters used in the best run of each model.

>>>>

We use random search to tune the hyperparameters of the model, setting the ranges for search for each hyperparameter heuristically (and validating the reasonableness of the ranges on the development set), and then launching eight copies of each experiment each with newly sampled hyperparameters from those ranges. Table~\ref{tab:hyperparams} below shows the hyperparameters used in the best run of each model.
